Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2018-06-28 SupportingInformation.Rmd
error fixed

```{r bivar_tab_summary_fn,echo=F}
bivar_tab_summary_fn<-function(r){

@@

  m$Indep.p<-round(r$IndepTestRes,3)
  m$`AIC-best.copula`<-r$InfCritRes$copname[which.min(r$InfCritRes$AIC)]
  m$Highest.AICw<-round(max(r$InfCritRes$AICw),3)
  m$N.AICw<-round(r$InfCritRes$AICw[1],3)
  m$p.CvM<-r$GofRes_CvM
  m$p.KS<-r$GofRes_KS
  m$LT_model.avg<-round(r$relLTdep_AICw,3)
  m$UT_model.avg<-round(r$relUTdep_AICw,3)
  m$`(LT-UT)_model.avg`<-m$LT_model.avg-m$UT_model.avg
  m$Rank_Pl_K<-r$Rank_Pl_K
  m$Rank_Pu_K<-r$Rank_Pu_K
  m$`Rank_Pl-Pu_K`<-r$Rank_PlmPu_K
  mt<-as.data.frame(t(m))
  return(mt)

}
#----------------------------------
#calling the above function on 3 multivariable datasets
m1<-bivar_tab_summary_fn(r=BivMS_res_Loecke)
m2<-bivar_tab_summary_fn(r=BivMS_BMR)
m3<-bivar_tab_summary_fn(r=BivMS_contrasts_67)
tab_bivar_summary<-cbind(m1,m2,m3)
colnames(tab_bivar_summary)<-c("SoilCN","BMR","Anolis")
saveRDS(tab_bivar_summary,"./Results/tab_bivar_summary.RDS")
```

>>>>

```{r bivar_tab_summary_fn,echo=F}
bivar_tab_summary_fn<-function(r,rs){

@@

  m$Indep.p<-round(r$IndepTestRes,3)
  m$`AIC-best.copula`<-r$InfCritRes$copname[which.min(r$InfCritRes$AIC)]
  m$Highest.AICw<-round(max(r$InfCritRes$AICw),3)
  m$N.AICw<-round(r$InfCritRes$AICw[1],3)
  m$p.CvM<-r$GofRes_CvM
  m$p.KS<-r$GofRes_KS
  m$LT_model.avg<-round(r$relLTdep_AICw,3)
  m$UT_model.avg<-round(r$relUTdep_AICw,3)
  m$`(LT-UT)_model.avg`<-m$LT_model.avg-m$UT_model.avg
  m$Rank_Pl_K<-rs$Rank_Pl_K
  m$Rank_Pu_K<-rs$Rank_Pu_K
  m$`Rank_Pl-Pu_K`<-rs$Rank_PlmPu_K
  mt<-as.data.frame(t(m))
  return(mt)

}
#----------------------------------
#calling the above function on 3 multivariable datasets
m1<-bivar_tab_summary_fn(r=BivMS_res_Loecke,rs=stat_soilCN_ga)
m2<-bivar_tab_summary_fn(r=BivMS_BMR,rs=stat_BMR_ga)
m3<-bivar_tab_summary_fn(r=BivMS_contrasts_67,rs=stat_contrasts_67_ga)
tab_bivar_summary<-cbind(m1,m2,m3)
colnames(tab_bivar_summary)<-c("SoilCN","BMR","Anolis")
saveRDS(tab_bivar_summary,"./Results/tab_bivar_summary.RDS")
```
